---
title: "3_plot_nnttrade"
output: html_document
date: "2024-02-19"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
```{r}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(deSolve)
library(ggplot2)
library(tidyr)
library(ggpubr)
library(ggmatplot)
library(RColorBrewer)
library(gridExtra)
library(cowplot)
library(viridis)
```


```{r}
tot_pop <- 30066648   ## Took population for 2020 from Mozambique INE (Institute of statistics)
p_urban <- 0.34 ##From INE
p_rural <- 1-p_urban
start.Ns <- c(10884513, 4883969, 7958844, 4900719, 992149, 446454)
dist <- start.Ns/tot_pop

pop_dist = data.frame(age_ur = c("cr","cu","ar","au","er","eu"),
                      pop = start.Ns)

old_pop <-  992149+446454
```

```{r}
scen_lab <- data.frame(sero_thresh = c("ann_late","bi_late","0","0.5","0.55","0.6","0.65","0.7","0.75","0.8"),
                       lab1 = c("Annual","Biennial","No vax","50% thresh","55% thresh", "60% thresh", "65% thresh","70% thresh","75% thresh","80% thresh"),
                       lab2 = c("Annual","Biennial","No vax","50%","55%", "60%", "65%","70%","75%","80%"))%>%
  mutate(lab1 = 
    factor(lab1, levels=c("No vax","Annual","Biennial","50% thresh","55% thresh","60% thresh",
              "65% thresh","70% thresh","75% thresh","80% thresh")),
         lab2 = 
    factor(lab2, levels =c("No vax", "Annual", "Biennial","50%", "55%", "60%","65%","70%","75%","80%")))

```


# First section on NNTs
```{r}
nnt_vaxsero   <- readRDS("0_res/vaxsero_nnt.RDS")
#nnt_vaxint  <- readRDS("0_res/vaxint_nnt.RDS") 
nnt_vaxsero_2500<- readRDS("../1_main0.7/0_res/vaxsero_nnt.RDS")%>%
                    filter(sweep_unique<=32)


nnt_main <- nnt_vaxsero%>%
              bind_rows(nnt_vaxsero_2500)

nnt_main <- nnt_main%>%
              mutate(kappa_lab = paste0("1/",kappa),
                     kappa_lab = factor(kappa_lab, c("1/500","1/1000","1/1500","1/2000","1/2500","1/3000","1/3500",NA)),
                     yr = firstvax/365)%>%
              left_join(scen_lab)


no_vax <- nnt_main%>%
          filter(sero_thresh==0)%>%
          select(sweep_unique, kappa, omega2, omega4, foi_sp,num_deaths,num_deaths_e)%>%
          dplyr::rename(.,num_deaths_novax=num_deaths)%>%
          dplyr::rename(.,num_deaths_e_novax=num_deaths_e)

nnt_main<- nnt_main%>%
            left_join(no_vax, by =c("sweep_unique","kappa","omega2","omega4","foi_sp"))


nnt_main <- nnt_main %>% 
            mutate(deaths_averted  = num_deaths_novax  -num_deaths,
                   deaths_averted_e= num_deaths_e_novax-num_deaths_e,
                   nnt=num_dose/deaths_averted,
                   nnt_e = num_dose/deaths_averted_e,
                   prop_red_e = deaths_averted_e/num_deaths_e_novax,
                   prop_red   = deaths_averted/num_deaths_novax,
                   dt_e_per100000 = (num_deaths_e/old_pop)*100000
                   )
              

```




## NNT and deaths for elderly only
```{r}
pal <- c("#201321FF","#3C3162FF","#3B589AFF","#3485A5FF","#3CB2ADFF","#81D8B0FF","#DEF5E5FF","#FCFDBFFF","#FDE4A6FF")
pal1 <- c("#201321FF","#3C3162FF","#3B589AFF","#3485A5FF","#3CB2ADFF","#81D8B0FF","#DEF5E5FF","#FDE4A6FF","#FECC8FFF")
pal2 <-  c("#201321FF","#3C3162FF","#3B589AFF","#3485A5FF","#81D8B0FF","#FFFFCC","#FFEDA0","#FDE4A6FF","#FECC8FFF","#FEC44F","#FE9929") 


theme_frame <- theme(panel.background = element_rect(fill = "white", colour = "black",size = 0.7, linetype = "solid"),
        panel.grid.major = element_line(size = 0.0001, linetype = 'solid',colour = "white"),
        panel.grid.minor = element_line(size = 0.0001, linetype = 'solid',
                                colour = "white"))

plot_theme <- plot_theme <- theme(plot.title = element_text(size=14),axis.ticks.x = element_blank(), axis.text.x = element_blank(),
                      axis.text = element_text(size=11),
                      axis.text.y = element_text(size=11),
                      axis.title = element_text(size=12),
 #                     strip.text = element_blank(),
                      legend.text = element_text(size=12),
                      legend.position = "right",legend.title = element_blank())+
  theme(plot.margin = unit(c(-0.5,0.2,-0.5,1), "line"))+ theme_frame
```

##Summary plots for sensitivity analysis on waning antibody rate
```{r}
abwane_med <- nnt_main%>%
  filter(!sero_thresh%in%c("0","ann_late","bi_late","0.55","0.65","0.75"))%>%
  filter(nnt_e>0&!is.na(kappa_lab))%>%
  group_by(kappa_lab,lab1)%>%
  summarise(nnt_med = median(nnt_e))


p1 <- abwane_med%>%
  ggplot(aes(x=lab1, y=nnt_med, col=kappa_lab))+
  geom_point(aes(x=lab1, y=nnt_med, col=kappa_lab),size=3)+
  geom_line(aes(x=lab1, y=nnt_med, col=kappa_lab,group=kappa_lab),size=0.7)+
  scale_y_log10()+
  scale_colour_manual(values = brewer.pal("BuPu",n=9)[9:3],name="")+
  geom_hline(yintercept =888, colour="orange1", linetype="dashed", size=1.0)+
  geom_hline(yintercept= 597, colour="lightgoldenrod1",linetype="dashed",size=1.0)+
  annotate("text", x=4.3, y=930, label="Annual NNV",size=4)+
  annotate("text", x=4.3, y=530, label="Biennial NNV",size=4)+
  #scale_color_identity()+
  theme_bw()+ylab("Median NNV")+xlab("Seroprevalence threshold for vaccination")+
  ggtitle("Summary vax efficiency by antibody waning rate")+
  theme(legend.position = "bottom", legend.text = element_text(size=12),
        axis.text = element_text(size=13),axis.title = element_text(size=14),
        plot.title=element_text(size=14))+ guides(colour = guide_legend(nrow = 1))


```

##Inset comparing waning rate of antibody with waning rate of immunity
```{r}
###From first infection
df <- data.frame(t=1:3650)%>%
      mutate(kappa=1,
             kappa1=lag(kappa)-lag(kappa)/500)

df$r3 <-1
df$s3 <-0
df$s2 <-0

for(t in 2:nrow(df)){
   df$r3[t] <- df$r3[t-1]-df$r3[t-1]/180
   df$s3[t] <- df$s3[t-1]+df$r3[t-1]/180-df$s3[t-1]/365
   df$s2[t] <- df$s2[t-1]+df$s3[t-1]/365
}

df<- df%>%mutate(imm = r3*1 +s3*(1-0.1)+s2*(1-0.4))

for(t in 2:nrow(df)){
  if(t==2){
    df$kappa0500[t]=df$kappa[t-1]-df$kappa[t-1]/500
  } else{
    df$kappa0500[t]=df$kappa0500[t-1]-df$kappa0500[t-1]/500
  }
}

for(t in 2:nrow(df)){
  if(t==2){
    df$kappa1000[t]=df$kappa[t-1]-df$kappa[t-1]/1000
  } else{
    df$kappa1000[t]=df$kappa1000[t-1]-df$kappa1000[t-1]/1000
  }
}

for(t in 2:nrow(df)){
  if(t==2){
    df$kappa1500[t]=df$kappa[t-1]-df$kappa[t-1]/1500
  } else{
    df$kappa1500[t]=df$kappa1500[t-1]-df$kappa1500[t-1]/1500
  }
}

for(t in 2:nrow(df)){
  if(t==2){
    df$kappa2000[t]=df$kappa[t-1]-df$kappa[t-1]/2000
  } else{
    df$kappa2000[t]=df$kappa2000[t-1]-df$kappa2000[t-1]/2000
  }
}

for(t in 2:nrow(df)){
  if(t==2){
    df$kappa2500[t]=df$kappa[t-1]-df$kappa[t-1]/2500
  } else{
    df$kappa2500[t]=df$kappa2500[t-1]-df$kappa2500[t-1]/2500
  }
}

for(t in 2:nrow(df)){
  if(t==2){
    df$kappa3000[t]=df$kappa[t-1]-df$kappa[t-1]/3000
  } else{
    df$kappa3000[t]=df$kappa3000[t-1]-df$kappa3000[t-1]/3000
  }
}

for(t in 2:nrow(df)){
  if(t==2){
    df$kappa3500[t]=df$kappa[t-1]-df$kappa[t-1]/3500
  } else{
    df$kappa3500[t]=df$kappa3500[t-1]-df$kappa3500[t-1]/3500
  }
}


p2 <- df%>%
  filter(t!=1)%>%
  mutate(t=t/365)%>%
  select(t,imm,kappa0500:kappa3500)%>%
  pivot_longer(cols=imm:kappa3500, names_to="var",values_to="val")%>%
  mutate(linetype = ifelse(var=="imm","immunity","sero"))%>%
  ggplot()+
  geom_line(aes(x=t, y=val, col=var,linetype=linetype),size=1.1)+
  scale_colour_manual(values = c("#F768A1",brewer.pal("BuPu",n=9)[9:3]))+
  scale_linetype_manual(values = c("solid",rep("dashed",7)), guide="none")+
  xlim(0,4)+ylim(0,1)+
  theme_classic()+
  xlab("Years since exposure")+
  ylab("Prop. pos")+
  ggtitle("Immunity & antibody waning input")+
  theme(legend.position="none",
        title = element_text(size=11),
        axis.text = element_text(size=11), axis.title = element_text(size=11))


```

##Combined plots for figure - new version
```{r}
##Inset
p3 <- ggdraw()+
  draw_plot(p1)+
  draw_plot(p2,x = 0.12, y = .63, width = .4, height = .3)

p4 <- readRDS("../1_main0.7/0_plot/0_plot_vaxfirst_deaths.RDS")+
      ggtitle("Death by first vax vs fixed interval strategies")+theme_bw()+
      theme(legend.position = "none", axis.text.x = element_blank(), axis.title.x = element_blank(),
             axis.text = element_text(size=12), axis.title = element_text(size=13), plot.title=element_text(size=14))
p5 <- readRDS("../1_main0.7/0_plot/0_plot_vaxfirst_nnt_e.RDS")+
      ggtitle("NNV by first vax vs fixed interval strategies")+theme_bw()+
      theme(legend.position="bottom", legend.title = element_blank(),
             axis.text = element_text(size=12), axis.title = element_text(size=13), plot.title=element_text(size=14))+ 
  guides(colour = guide_legend(nrow = 1))



png("0_plot/1_fig4a.png",width=13,height=7, units="in",res=700)
grid.arrange(p3,p4,p5,ncol=7,nrow=7,
             layout_matrix=rbind(c(2,2,2,1,1,1,1),
                                 c(2,2,2,1,1,1,1),
                                 c(2,2,2,1,1,1,1),
                                 c(3,3,3,1,1,1,1),
                                 c(3,3,3,1,1,1,1),
                                 c(3,3,3,1,1,1,1),
                                 c(3,3,3,1,1,1,1)))
#grid.arrange(p99,p3,ncol=1,nrow=2,
#             layout_matrix=rbind(1,2))
#plot_grid(p99,p3, align="h")
dev.off()

p1b <- p1+theme(legend.position="right")+ guides(colour = guide_legend(ncol = 1))
p3b <- ggdraw()+
  draw_plot(p1b)+
  draw_plot(p2,x = 0.12, y = .63, width = .4, height = .3)
p4b <- readRDS("../1_main0.7/0_plot/0_plot_vaxfirst_deaths.RDS")+
      ggtitle("Death by first vax vs fixed interval strategies")+theme_bw()+
      theme(legend.position="none", legend.title = element_blank())

p5b <- p5+
      theme(legend.position="right", legend.title = element_blank())

png("0_plot/1_fig4b.png",width=11,height=7, units="in",res=700)
grid.arrange(p3b,p4b,p5b,ncol=5,nrow=4,
            layout_matrix=rbind(c(1,1,1,1,1),
                                c(1,1,1,1,1),
                                c(2,2,3,3,3),
                                c(2,2,3,3,3)))
#grid.arrange(p99,p3,ncol=1,nrow=2,
#             layout_matrix=rbind(1,2))
#plot_grid(p99,p3, align="h")
dev.off()
```


##Combined plots for Figure 4 original version
```{r}
##Inset
p3 <- ggdraw()+
  draw_plot(p1)+
  draw_plot(p2,x = 0.15, y = .63, width = .51, height = .3)

png("0_plot/1_fig4a.png",width=11,height=5, units="in",res=700)
grid.arrange(p3,p99,ncol=8,nrow=2,
             layout_matrix=rbind(c(1,1,1,1,2,2,2,2),c(1,1,1,1,2,2,2,2)))
#grid.arrange(p99,p3,ncol=1,nrow=2,
#             layout_matrix=rbind(1,2))
#plot_grid(p99,p3, align="h")
dev.off()


```


## Summary table
```{r}


tab1 <- nnt_main%>%
  #filter(nnt>0)%>%
  #filter(!sweep_unique %in% nnt_neg_rem)%>%
  group_by(sero_thresh,foi_sp,kappa)%>%
  dplyr::summarise(nnt_med=median(nnt,na.rm = T),
            nnt_25 = quantile(nnt,probs=0.025, na.rm = T),
            nnt_75 = quantile(nnt, probs=0.975, na.rm=T),
            nnt_e_med = median(nnt_e, na.rm=T),
            nnt_e_25 = quantile(nnt_e,probs=0.025, na.rm = T),
            nnt_e_75 = quantile(nnt_e, probs=0.975, na.rm=T),
            num_camp_med = median(num_campaigns, na.rm=T),
            num_camp_25 = quantile(num_campaigns, probs=0.025, na.rm=T),
            num_camp_75 = quantile(num_campaigns, probs=0.975, na.rm=T),
            dt_avert_e_med = median(deaths_averted_e, na.rm=T),
            dt_avert_e_25 = quantile(deaths_averted_e, probs=0.025, na.rm=T),
            dt_avert_e_75 = quantile(deaths_averted_e, probs=0.975, na.rm=T),
            dt_avert_med = median(deaths_averted, na.rm=T),
            dt_avert_25 = quantile(deaths_averted, probs=0.025, na.rm=T),
            dt_avert_75 = quantile(deaths_averted, probs=0.975, na.rm=T),
            dt_med = median(num_deaths, na.rm=T),
            dt_25 = quantile(num_deaths, probs=0.025, na.rm=T), 
            dt_75 = quantile(num_deaths, probs=0.975, na.rm=T),
            dt_e_med = median(num_deaths_e, na.rm=T),
            dt_e_25 = quantile(num_deaths_e, probs=0.025, na.rm=T), 
            dt_e_75 = quantile(num_deaths_e, probs=0.975, na.rm=T),
            dt_e_percap_med = median(dt_e_per100000,na.rm=T),
            dt_e_percap_25 = quantile(dt_e_per100000, probs=0.025, na.rm=T),            
            dt_e_percap_75 = quantile(dt_e_per100000, probs=0.975,na.rm=T),            
            firstvax_med =median(firstvax, na.rm=T),
            firstvax_25 = quantile(firstvax, probs=0.025, na.rm=T),
            firstvax_75 = quantile(firstvax, probs=0.975, na.rm=T),
            prop_red_med    = median(prop_red),
            prop_red_25 = quantile(prop_red, probs=0.025, na.rm=T),
            prop_red_75 = quantile(prop_red, probs=0.975, na.rm=T),
            prop_red_e_med    = median(prop_red_e),
            prop_red_e_25 = quantile(prop_red_e, probs=0.025, na.rm=T),
            prop_red_e_75 = quantile(prop_red_e, probs=0.975, na.rm=T))%>%
            
            #nnt_med_p2 = median(nnt_post2, na.rm=T),
            #nnt_25_p2 = quantile(nnt_post2, probs=0.25, na.rm=T),
            #nnt_75_p2 = quantile(nnt_post2, probs=0.75, na.rm=T)) 
  
  mutate(NNT = paste(round(nnt_med, digits=0)," (", round(nnt_25, digits=0),"-",round(nnt_75, digits=0),")", sep=""),
         NNT_e = paste(round(nnt_e_med, digits=0)," (", round(nnt_e_25, digits=0),"-",round(nnt_e_75, digits=0),")", sep=""),
         NumCampaign = paste(round(num_camp_med, digits=0)," (", round(num_camp_25, digits=0),"-",round(num_camp_75,digits=0),")", sep=""),
         DeathsAverted = paste(round(dt_avert_med, digits=0)," (", round(dt_avert_25, digits=0),"-",round(dt_avert_75, digits=0),")", sep=""),
         DeathsAverted_e = paste(round(dt_avert_e_med, digits=0)," (", round(dt_avert_e_25, digits=0),"-",round(dt_avert_e_75, digits=0),")", sep=""),
         Deaths = paste(round(dt_med, digits=0)," (", round(dt_25, digits=0),"-",round(dt_75, digits=0),")", sep=""),
         Deaths_e = paste(round(dt_e_med, digits=0)," (", round(dt_e_25, digits=0),"-",round(dt_e_75, digits=0),")", sep=""),

         FirstVaxTime = paste(round(firstvax_med)," (",round(firstvax_25),"-",round(firstvax_75),")", sep=""),
         prop_red_e_med = paste(round(prop_red_e_med*100, digits=0), "%", sep=""),
         prop_red_med = paste(round(prop_red_med*100, digits=0), "%"))%>%

  #left_join(scen_lab, by="scen")%>%
  select( sero_thresh,kappa,foi_sp,NNT_e, DeathsAverted_e,prop_red_e_med, Deaths_e, NNT, DeathsAverted,Deaths, NumCampaign, DeathsAverted, Deaths,FirstVaxTime)

#write.csv(tab1, "0_plot/1_nnt_95.csv")
## res for children and adults
nnt_main%>%
  group_by(sero_thresh)%>%
  dplyr::summarise(
            prop_red_med    = median(prop_red),
            prop_red_25 = quantile(prop_red, probs=0.025, na.rm=T),
            prop_red_75 = quantile(prop_red, probs=0.975, na.rm=T),
            prop_red_e_med    = median(prop_red_e),
            prop_red_e_25 = quantile(prop_red_e, probs=0.025, na.rm=T),
            prop_red_e_75 = quantile(prop_red_e, probs=0.975, na.rm=T))

tab1%>%arrange(kappa)
```



```{r}
p11o <- nnt_main%>%
       left_join(scen_lab)%>%
       filter(sero_thresh!="0"&!is.na(lab2))%>%  
  ggplot(aes(x=lab2, y=nnt_e, fill=lab2, text=lab2))+
  #ggplot(aes(x=sero_thresh, y=nnt_e, fill=sero_thresh, text=sero_thresh))+
  geom_violin(width=1, size=0.2)+
  scale_fill_manual(values = rev(pal1))+
  scale_color_manual(values=rev(pal1))+
  ylim(0,2000)+
 theme_classic()+
  theme(axis.text.x = element_text(vjust=0.8, hjust=0.5, size=13),
        axis.text.y = element_text(size=13),
        axis.title = element_text(size=13),
        plot.title = element_text(size=13),
        legend.position="none")+
  theme_frame+
  coord_flip()+
  ylab("No. of doses needed to avert one death")+xlab("Vaccination timing")+
  ggtitle("Number of vaccine doses needed to avert one death")

##Age-specific death distribution by vax scenario
age_death <- nnt_main %>%
  left_join(scen_lab)%>%
  filter(!is.na(lab2))%>%  
  select(lab2, num_deaths_c:num_deaths_e)%>%
  pivot_longer(cols=num_deaths_c:num_deaths_e, names_to="var", values_to="val")%>%
  group_by(lab2,var)%>%
  dplyr::summarise(death_med=median(val),
            death_25 = quantile(val, probs=0.25),
            death_75 = quantile(val, probs=0.75))%>%
  left_join(data.frame(var =c("num_deaths_c","num_deaths_a","num_deaths_e"),
                       age_grp = c("Child","Adult","Adult >50 yr")))%>%
  mutate(age_grp = factor(age_grp, level=c("Adult >50 yr","Adult","Child")))

death_e <- age_death %>%
        filter(var=="num_deaths_e")

p12o <- death_e%>%
  filter(var=="num_deaths_e")%>%
  ggplot()+
  geom_col(aes(x=lab2,y=death_med), fill="#006D2C", width=0.7, alpha=0.55)+
geom_errorbar(data=death_e, aes(x=lab2, ymin=death_25, ymax=death_75), width=0.3, size=0.7, color="gray50")+
  coord_flip()+
 theme_classic()+
ylab("Deaths")+xlab("")+ggtitle("10-yr cumulative deaths (older adults)")+
    theme(plot.title = element_text(size=14),
                      axis.text.x = element_text(size=13),
                      axis.text.y = element_text(size=11, hjust=1),
                      axis.title = element_text(size=13),
                     legend.position="right")+
    theme_frame

png("0_plot/9_res_waninghi_older.png", width = 12,height = 4,units="in",res=500)
as_ggplot(arrangeGrob(p11o,p12o,nrow=1,ncol =6, layout_matrix=rbind(c(1,1,1,2,2,2))))
dev.off()

saveRDS(p11o,"0_plot/0_plot_nnt_e.RDS")  ##save plot objects to be read into the other rmd
saveRDS(p12o,"0_plot/0_plot_deaths_e.RDS")

```


##FIrst time vax vs vaccine efficiency
```{r}

pal1 <- c("#201321FF","#3C3162FF","#3B589AFF","#3485A5FF","#3CB2ADFF","#81D8B0FF","#DEF5E5FF","#FDE4A6FF","#FECC8FFF")[c(7,5,3,1)]


p99 <- nnt_main%>%
  filter(!sero_thresh%in%c("0","ann_late","bi_late"))%>%
  filter(nnt_e>0&!is.na(kappa_lab))%>%
  ggplot(aes(x=yr, y=nnt_e, col = as.factor(lab1)))+
  geom_point()+ 
  #stat_cor(p.accuracy = 0.001, r.accuracy = 0.01)+
  #geom_text(aes(x=-Inf,y=Inf,hjust=0,vjust=1,label=paste("R-squared =",cor(df_corr_novax$tot_death, df_corr_novax$e))), colour="black")+
  ggtitle("Vaccine efficiency by assumed antibody waning rate")+
  scale_y_log10()+
  geom_hline(yintercept =888, colour="orange1", linetype="dashed", size=1.0)+
  geom_hline(yintercept= 597, colour="lightgoldenrod1",linetype="dashed",size=1.0)+
  scale_color_manual(values = pal1, name="Vax scenario")+
  theme_classic()+
  theme(legend.position = "bottom",
        legend.title = element_text(size=10),
        legend.text = element_text(size=10),
        axis.text.y = element_text(size=9),
        axis.text.x = element_text(size=11),
        strip.text = element_text(size=11))+
  ylab("NNV")+xlab("Time of first vaccine (Yrs)")+
  facet_wrap(~kappa_lab, scales="free_y")

png("0_plot/timefirstvax_nnt.png", width = 10,height = 6,units="in",res=600)
p99
dev.off()
```

## Yearly cumulative NNT
```{r}
viridis(20, alpha = 1, begin = 0, end = 1, direction = 1, option = "A")
pal1 <- c("#201321FF","#3C3162FF","#3B589AFF","#3485A5FF","#3CB2ADFF","#81D8B0FF","#DEF5E5FF","#FDE4A6FF","#FECC8FFF")

nnt_yr <- readRDS("0_res/orig/vaxsero_nntyr.RDS")
nnt1_yr<-readRDS("0_res/orig/vaxint_nntyr.RDS")

nnt_yr%>%filter(sweep_unique==33&sero_thresh=="0.8")
nnt_yr%>%filter(sweep_unique==33&sero_thresh=="0.5")

```

```{r}

nnt_yr <- nnt_yr %>%
  #filter(yr!=10)%>%
  group_by(sero_thresh, sweep_unique)%>%
  replace(is.na(.),0)%>%
  mutate(num_dose_roll = cumsum(num_dose))
nnt_yr_novax <- nnt_yr %>%filter(sero_thresh=="0")%>%
                  ungroup()%>%
                  select(sweep_unique, yr, new_Deaths_e_roll, new_Deaths_tot_roll)%>%
                  dplyr::rename("new_Deaths_e_roll_novax"="new_Deaths_e_roll")%>%
                  dplyr::rename("new_Deaths_tot_roll_novax"="new_Deaths_tot_roll")

nnt_yr <- nnt_yr %>% left_join(nnt_yr_novax, by=c("sweep_unique"="sweep_unique","yr"="yr"))%>%
            mutate(nnt_e_yr = num_dose_roll/(new_Deaths_e_roll_novax-new_Deaths_e_roll),
                   nnt_tot_yr = num_dose_roll/(new_Deaths_tot_roll_novax-new_Deaths_tot_roll))%>%
            filter(sero_thresh!="0")

nnt1_yr <- nnt1_yr %>%
          #filter(yr!=10)%>%
          group_by(sero_thresh, sweep_unique)%>%
          replace(is.na(.),0)%>%
          mutate(num_dose_roll = cumsum(num_dose))%>%
            left_join(nnt_yr_novax, by=c("sweep_unique"="sweep_unique", "yr"="yr"))%>%
            mutate(nnt_e_yr = num_dose_roll/(new_Deaths_e_roll_novax-new_Deaths_e_roll),
                   nnt_tot_yr = num_dose_roll/(new_Deaths_tot_roll_novax-new_Deaths_tot_roll))
  
nnt_yr_med <- nnt_yr %>%
  mutate(sero_thresh=as.character(sero_thresh))%>%
  rbind(nnt1_yr)%>%
  mutate(yr1=yr+1)%>%
  group_by(yr1,yr, sero_thresh)%>%
  dplyr::summarise(med = median(nnt_e_yr, na.rm=T))%>%
   mutate(sero_thresh = factor(sero_thresh,
          levels = c("ann_late","bi_late","0.5","0.55","0.6", "0.65","0.7","0.75","0.8")))%>%
  arrange(sero_thresh)

nnt_yr_med

```

```{r}
lab = c("50%","55%", "60%", "65%","70%","75%","80%","Annual","Biennial")
pal3 <- c("#DEF5E5FF","#81D8B0FF","#3CB2ADFF","#3485A5FF","#3B589AFF","#3C3162FF","#201321FF","#FDE4A6FF","#FECC8FFF")


##Main one for output
nnt_death_trade <- nnt_main %>%
  filter(!sero_thresh%in%c("0","ann_435","bi_435","ann_800","bi_800"))%>%
  ggplot(aes(x=num_deaths_e, y=nnt_e, col=sero_thresh))+
  scale_fill_manual(values = pal3,labels = lab)+
  scale_color_manual(values= pal3,labels = lab)+
  #scale_color_viridis(discrete=T, option="G", direction=-1, alpha=1)+
  #scale_fill_viridis(discrete=T, option="G", direction=-1, alpha=0.5)+
  geom_point()+
  xlim(0,11000)+ylim(0,2000)+
  theme_bw() + xlab("Number of deaths among older adults")+ylab("NNT among older adults")+
  theme(legend.title = element_blank(), 
        legend.position = "none",
        axis.text = element_text(size=12),
        axis.title=element_text(size=13),
        plot.title=element_text(size = 14))+
        ggtitle("Tradeoff in efficiency and no. deaths")
  
saveRDS(nnt_death_trade,"0_plot/0_nnt_death_trade.RDS")

nnt_yr_trade<-nnt_yr_med%>%  
  filter(!is.na(sero_thresh))%>%
  ggplot(aes(x=yr, y=med, col=sero_thresh))+
  #scale_fill_manual(values = rev(pal1),labels = lab)+
  #scale_color_manual(values=rev(pal1),labels = lab)+
  scale_fill_manual(values = rev(pal1))+
  scale_color_manual(values=rev(pal1))+
  scale_x_continuous(breaks = seq(from = 1, to = 10, by = 1))+
  xlim(1,10)+
  coord_trans(y = "log10")+
  #ylim(0,4000)+
  #scale_color_viridis(discrete=T, option="G", direction=-1, alpha=1)+
  geom_line(size=1, linetype="dashed")+
  geom_point(size=2.5)+theme_bw()+
  theme(legend.title=element_blank(),
        #legend.position = "none",
        axis.text = element_text(size=12),
        axis.title=element_text(size=13),
        plot.title=element_text(size = 14))+
  xlab("Year")+ylab("Cumulative NNT (median)")+
  ggtitle("Tradeoffs in efficiency over time")

#png("0_plot/3_nnt_trade.png", width = 11,height = 4,units="in",res=600)
as_ggplot(arrangeGrob( nnt_yr_trade, nnt_death_trade,nrow=2,ncol =2, 
                      layout_matrix=rbind(c(1,2), c(1,2))))
#dev.off()

unique(nnt1_yr$sero_thresh)
```


##NNT death tradeoff
```{r}

## Other explorations
nnt_main <- nnt_main%>%mutate(yr = firstvax/365)
                     
p10 <- nnt_main%>%
    filter(!sero_thresh%in%c("0","ann_late","bi_late","ann_435","bi_435","ann_800","bi_800"))%>%
  #filter(!scen%in%c("No vax","ann_late","bi_late"))%>%
  ggplot(aes(x=yr, y=nnt, col=sero_thresh))+
  scale_color_manual(values = rev(pal1)[3:9])+
  ylim(0,3000)+
  geom_point()+
  #geom_point(aes(x=300/365,y=1941),colour="red",size=6, shape=18)+
  #geom_point(aes(x=300/365,y=1443),colour="orange",size=6, shape=18)+
  geom_point(aes(x=300/365,y=946),colour="orange",size=6, shape=18)+
  geom_point(aes(x=300/365,y=674),colour="#FDE4A6FF",size=6, shape=18)+
  geom_hline(yintercept =946, color="orange", linetype="dashed", size=0.8)+
  geom_hline(yintercept= 674, color="#FDE4A6FF",linetype="dashed",size=0.8)+
  ylab("Number needed to treat (NNT) among older adults")+xlab("Year of first campaign")+
  theme_bw()

png("0_plot/scatter_yrfirst_nnt.png", width = 6,height = 4,units="in",res=300)
p10
dev.off()


```

